Evaluation

### 2018-12-03 evaluation.Rmd
Remove unused tools

model_metadata = yaml.load_file("forecasting/data/model_metadata.yaml")
pred_interval = model_metadata$pred_interval
models_of_interest = c('AutoArima','Ensemble','ESSS','nbGARCH','pevGARCH')

>>>>

model_metadata = yaml.load_file("forecasting/data/metadata.yaml")
pred_interval = model_metadata$pred_interval
models_of_interest = c('AutoArima','Ensemble','ESSS','nbGARCH','pevGARCH')
